---
title: "Delirium Harmonization: 3D-CAM"
author: "Doug Tommet"
date: '`r Sys.Date()`'
format:
  html:
    toc: true
    self-contained: true
    theme: journal
figures:
  fig-cap-location: top 
execute:
  echo: false
  warning: false
  message: false
keep-md: true
---

```{r}
source(here::here("R", "001-Libraries_and_functions.R"))
source(here::here("R", "005-folder_paths.R"))
```

```{r}
combined_df <- readRDS(file=fs::path(r_objects_folder, "025_combined_df.rds"))
sages_del_assessment <- readRDS(file=fs::path(r_objects_folder, "020_sages_del_assessment.rds"))

intuit_cog_df <- readxl::read_xlsx(fs::path(duke_data_folder, "MADCOPC_INTUIT_forNIDUS_04142022.xlsx"), sheet = "CognitiveData")

intuit_cog_df <- intuit_cog_df %>%
  filter(study=="I") %>%
  filter(visit==0)

sages_interview <- haven::read_dta(fs::path(sagesI_datafolder, "SAGES-Subject-Interview-Data-Analysis-File.dta"))
sages_560 <- read_csv(fs::path(sagesI_datafolder, "N560.csv"))
```

# Comparison of MMSE scores.

```{r}
intuit_cog_df %>%
  select(mmsetot) %>%
  gtsummary::tbl_summary(
    type = c(mmsetot) ~ "continuous2",
    statistic = list(
      gtsummary::all_continuous() ~ c(
      "{N_nonmiss}",
      "{mean} ({sd})",
      "{median} ({p25}, {p75})",
      "{min}, {max}"
    ),
      gtsummary::all_categorical() ~ "{n} / {N} ({p}%)"
    )
  )

sages_interview %>%
  filter(timefr==0) %>%
  filter(studyid %in% (sages_560 %>% pull(studyid))) %>%
  select(vdmmse) %>%
  gtsummary::tbl_summary(
    type = c(vdmmse) ~ "continuous2",
    statistic = list(
      gtsummary::all_continuous() ~ c(
      "{N_nonmiss}",
      "{mean} ({sd})",
      "{median} ({p25}, {p75})",
      "{min}, {max}"
    ),
      gtsummary::all_categorical() ~ "{n} / {N} ({p}%)"
    )
  )
```

# Item recoding in SAGES

This section shows the recoding of the CAM items in SAGES to match the 3D-CAM item responses.

## What is the year?

Refusals and Don't knows count as errors.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q1_result, cf01)
```

## What is the day of week?

Refusals and Don't knows count as errors.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q2_result, cf04)
```

## What type of place are you in?

Refusals and Don't knows count as errors.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q3_result, cf06)
```

## Digit span: 3 backwards

Refusals count as errors, Unables count as missing.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(q4_errors, db3)
```

## Digit span: 4 backwards

Refusals count as errors, Unables count as missing.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(q5_errors, db4)
```

## Days of the week backwards

Refusals and Don't knows count as errors.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(q6_errors, dow_total_correct)
```

## Months of the year backwards

Refusals and Don't knows count as errors.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(q7_errors, moy_total_correct)
```

## Have you felt confused today?

Refusals and Don't knows count as missing.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q8_result, dsi02)
```

## Did you think you weren't in the hospital?

Refusals and Don't knows count as missing.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q9_result, dsi01)
```

## Did you see things that weren't really there?

Refusals and Don't knows count as missing.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q10_result, dsi03)
```

## Patient sleepy, stuporouos or comatose?

Lethargic, stupor, coma count as present.
```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q11_result, cam03a)
```

## Patient hypervigilant?

Vigilant counts as a Yes.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q12_result, cam03a)
```

## Disorganized speech?

Mild, moderate, severe count as present.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q13_result, cam02a)
```

## Rambling conversation?

Doesn't seem like there is a good match in SAGES.

## Speech limited, sparse?

Doesn't seem like there is a good match in SAGES.

## Did patient have trouble keeping track during the interview?

Mild, moderate, severe count as present.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q16_result, cam01a)
```

## Easily distracted?

Doesn't seem like there is a good match in SAGES.

## Fluctuating level of consciousness

Uncertain counts as missing. Cam03a=="Alert" counts as No.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q18_result, cam03b)
```

## Fluctuating attention

Uncertain counts as missing. Cam02a=="Not present" counts as No.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q19_result, cam01b)
```

## Fluctuating speech

Uncertain counts as missing. Cam01a=="Not present" counts as No.

```{r}
sages_del_assessment %>%
  labelled::to_factor() %>%
  gtsummary::tbl_cross(dcam_q20_result, cam02b)


```

# Item comparison between studies

```{r}
combined_df %>%
  select(study, dcam_q1_result, dcam_q2_result, dcam_q3_result,
         q4_errors, q5_errors, q6_errors, q7_errors,
         dcam_q8_result, dcam_q9_result, dcam_q10_result, dcam_q11_result, dcam_q12_result,
         dcam_q13_result, dcam_q14_result, dcam_q15_result, dcam_q16_result, dcam_q17_result,
         dcam_q18_result, dcam_q19_result, dcam_q20_result) %>%
  labelled::to_factor() %>%
  gtsummary::tbl_summary(by = study)

```

